---
title: "Haddock S-R models"
author: "David Keith"
date: "11/14/2021"
output:
  bookdown::word_document2: default
  #bookdown::pdf_document2: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 999)
library(tidyverse)
library(cowplot)
library(lme4)
library(arm)
library(mgcv)
theme_set(theme_bw(base_size = 14))
# Load in the data.
dat <- readxl::read_xlsx("D:/Github/Haddock/Data/Stock_recruit_long_all.xlsx",sheet = "data")
# This is dumb... but I want it starting with a capital and I'm lazy
dat$Species <- dat$species
# Get the Rec/SSB value
dat$rec.ssb <- dat$recruits/dat$ssb
dat$log.r.ssb <- log(dat$rec.ssb)
# Get the maximum SSB for each stock, tidyverse mutate is so smart here...
dat <- dat %>% dplyr::group_by(stock) %>% dplyr::mutate (max.ssb= max(ssb))
dat$ssb.prop <- dat$ssb/dat$max.ssb
dat <- as.data.frame(dat)
dat <- dat %>% dplyr::group_by(stock) %>% dplyr::mutate(rssb.stan = as.numeric(scale(rec.ssb)),
                                                        log.rssb.stan = as.numeric(scale(log.r.ssb)))
dat$l.rec <- log10(dat$recruits)
dat$Period <- "Pre 1993"
dat$Period[dat$year >= 1993] <- "Recent"
dat$Period <- as.factor(dat$Period)
cols <- c("firebrick1","darkblue")
lty <- c("solid","dashed")
dat$alpha <- NA
dat$alpha.sd <- NA
dat$resids <- NA

# Now I need to get the recruits to all be 1 year olds, this is how to get there from the current data and assuming m = 0.2 and F = 0.  May
# need tweaked based on what Edda finds.
# The NS Haddock is Age 0, so multiply by 0.2
m <- 0.2
dat$recruits[dat$stock == "Haddock North Sea"] <- (1-m) * dat$recruits[dat$stock == "Haddock North Sea"]
# Irish Cod is Age 0so we need to step it back two years to get to 1 year olds
dat$recruits[dat$stock == "Haddock Irish Sea"] <- (1-m) * dat$recruits[dat$stock == "Haddock Irish Sea"]

# Icelandic Cod is Age 3 so we need to step it back two years to get to 1 year olds
dat$recruits[dat$stock == "Cod Icelandic"] <- dat$recruits[dat$stock == "Cod Icelandic"] / ((1-m)*(1-m)) 
# Icelandic Haddock is Age 2, so just one year back
dat$recruits[dat$stock == "Haddock Icelandic"] <- dat$recruits[dat$stock == "Haddock Icelandic"] / (1-m) 
# Barents Sea Haddock is Age 3, so two steps back
dat$recruits[dat$stock == "Haddock Barents Sea"] <- dat$recruits[dat$stock == "Haddock Barents Sea"] / ((1-m)*(1-m)) 
# Barents Sea Cod is also Age 3, so two steps back
dat$recruits[dat$stock == "Cod Barents Sea"] <- dat$recruits[dat$stock == "Cod Barents Sea"] / ((1-m)*(1-m)) 

# All other NE Atlantic stocks and all of the NW Atlantic stocks are Age 1 recruits


# Lets just stick with the most recently assessed.  
dat <- dat %>% dplyr::filter(Assessment == 'Current')
# And we'll toss the W of Scotland and the combo WoS + NS stocks as there is no Haddock stock to match.
dat <- dat %>% dplyr::filter(!stock %in% c("Cod North Sea + W. of Scot.","Cod West of Scotland"))

dat$stock <- factor(dat$stock,levels = c("Haddock Icelandic","Cod Icelandic","Haddock  Faroese","Cod Faroese","Haddock Barents Sea","Cod Barents Sea" ,
                                         "Haddock Irish Sea","Cod Irish Sea","Haddock North Sea","Cod North Sea",
                                         "Haddock Eastern Scotian Shelf","Cod Eastern Scotian Shelf","Haddock Western Scotian Shelf","Cod Western Scotian Shelf",
                                         "Haddock Eastern Georges Bank" , "Cod Eastern Georges Bank"))

dat$location[dat$location=="Icelandic"] <- "Iceland"

dat$location <- factor(dat$location,levels = c("Iceland","Faroese","Barents Sea",
                                               "Irish Sea","North Sea",
                                               "Eastern Georges Bank", "Western Scotian Shelf","Eastern Scotian Shelf"))

# Removing that crazy Haddock point in 2013 for WSS Haddock does nothing to the fit, which is bizarre, but it matches expecations from the rest of the data somehow?
#dat <- dat[!(dat$stock == "Haddock Western Scotian Shelf" & dat$year == 2013),]




```

# Fogarty Analysis

Fogarty re-analysis Figure 1

This analysis will compare recruitment between the primary harvested sympatric Atlantic Cod and Haddock stocks in the Atlantic Ocean, comparing the period before 1993 (*Pre-1993 Period*) with the period from 1993 onwards (*Recent Period*), data shown in Figure \@ref(fig:fog-rec). This is Figure 1 from Fogarty

```{r fog-rec, warning=F,echo =F,fig.width=11,fig.height=11,fig.cap= "Recruitment (in millons) time series for 8 Atlantic Cod (solid line) and Haddock (dashed line) stocks in the Atlantic Ocean.  The red line indicates data from the Pre-1993 Period, while the blue line is for the Recent Period. The vertical grey line indicates the division between the two periods"}
# Recruits vs SSB
p0 <- ggplot(dat %>% dplyr::filter(region == "Northeast Atlantic")) + geom_line(aes(y=recruits/1000, x= year,colour = Period,linetype = Species)) + 
              facet_wrap(~location ,scales = 'free',ncol=3) + xlab("") + ylab("Recruits (Number in Millons)")  + 
              scale_color_manual(values = cols)  + scale_linetype_manual(values = lty) + scale_y_log10() + 
              scale_x_continuous(limits = c(1945,2020),breaks = seq(1950,2020,by=10)) +
              geom_vline(xintercept = 1992.5,color = "grey",size =2) + 
              theme(axis.title.y = element_text(hjust=0),
                    legend.position = c(0.85, 0.25), 
                    legend.title.align=1,
                    legend.text.align = 1,
                    legend.title = element_text(size=16),
                    legend.text = element_text(size=12),
                    legend.key.width = unit(3,"cm")) + guides(colour = guide_legend(override.aes = list(size=1.5),title.position = "top"),
                                                              linetype = guide_legend(override.aes = list(size=1.5)))

# Now the NW Atlantic stocks
p1 <- ggplot(dat %>% dplyr::filter(region == "Northwest Atlantic")) + geom_line(aes(y=recruits/1000, x= year,colour = Period,linetype = Species)) + 
              facet_wrap(~ location ,scales = 'free',ncol=3) + xlab("Year") + ylab("")  + 
              scale_color_manual(values = cols)  + scale_linetype_manual(values = lty) + scale_y_log10() + 
              scale_x_continuous(limits = c(1945,2020),breaks = seq(1950,2020,by=10)) +
              geom_vline(xintercept = 1992.5, color ='grey',size=3)+
              theme(legend.position = "none")

p.rec.ts <- plot_grid(p0,p1,nrow=2,rel_heights = c(2,1))
p.rec.ts
```


\newpage

Next up was a simple stock-recruitment model using the linearization of the Ricker SR model.

$$ log\left(\frac{Rec}{SSB}\right) = log(a) - b\times SSB + \epsilon_i$$




```{r mods, echo =F,include =F,warning=F}
# The cod model
#summary(mod.stan)
#plot(mod.stan)
#ranef(mod.stan)
#se.ranef(mod.stan)
# Split the data into the 2 time series
dat.pre <- dat %>% dplyr::filter(Period == 'Pre 1993')
dat.recent <- dat %>% dplyr::filter(Period == 'Recent')
dat.all <- NULL
# Get the stocks ready for the loop
stocks <- unique(dat$stock)
n.stocks <- length(stocks)
# And run the S-R model for each stock/era individually.

# This is the analysis for the Alpha calculations.
for(i in 1:n.stocks)
{
  # Filter the data into the pre and recent periods for the alpha analysis
  pre.d <- dat.pre %>% filter(stock == stocks[i])
  recent.d <-        dat.recent %>% filter(stock == stocks[i])
  # Now run the models, but only run if you have data (i.e. Irish pre Cod has not data)
  if(nrow(pre.d) > 0) mod.pre <-   lm(log.r.ssb ~ ssb, data= pre.d)
  mod.recent <-      lm(log.r.ssb ~ ssb, data= recent.d)
  # Now stick the data back into the data frames, first the alphas and their Standard Deviation from the model
  if(nrow(pre.d) > 0) dat.pre$alpha[dat.pre$stock == stocks[i]] <- coefficients(mod.pre)[1]
  if(nrow(pre.d) > 0) dat.pre$alpha.sd[dat.pre$stock == stocks[i]] <- summary(mod.pre)$coefficients[1,2]
  dat.recent$alpha[dat.recent$stock == stocks[i]] <- coefficients(mod.recent)[1]
  dat.recent$alpha.sd[dat.recent$stock == stocks[i]] <- summary(mod.recent)$coefficients[1,2]
  # Now the residuals
  if(nrow(pre.d) > 0) dat.pre$resids[dat.pre$stock == stocks[i]] <- residuals(mod.pre)
  dat.recent$resids[dat.recent$stock == stocks[i]] <-    residuals(mod.recent)
  
  # Now we also have a model which fits the full time series of the Ricker model, this is the one we are going to use for the residual figures and the ACF calculations.
  dat.tmp <- dat %>% filter(stock == stocks[i])
  mod.all <- lm(log.r.ssb ~ ssb, data= dat.tmp)
  dat.tmp$alpha <- as.numeric(coefficients(mod.all)[1])
  dat.tmp$alpha.sd <- summary(mod.all)$coefficients[1,2]
  dat.tmp$resids <- residuals(mod.all)
  dat.all[[stocks[i]]] <- dat.tmp
}


# So North Sea Haddock and Western SS Haddock are both wild... Let's look closer at them...
dat.alpha <- bind_rows(dat.pre,dat.recent)
dat.alpha$alpha.exp <- exp(dat.alpha$alpha)
dat.alpha$LCI <- dat.alpha$alpha - 1.96 *dat.alpha$alpha.sd
dat.alpha$UCI <- dat.alpha$alpha + 1.96 *dat.alpha$alpha.sd

# Now we do the same thing for what I'll call dat.all.mod, which is ricker fit to full time series.  This is where we'll want to house all the residuals
dat.all.mod <- do.call('rbind',dat.all)
dat.all.mod$alpha.exp <- exp(dat.all.mod$alpha)
dat.all.mod$LCI <- dat.all.mod$alpha - 1.96 *dat.all.mod$alpha.sd
dat.all.mod$UCI <- dat.all.mod$alpha + 1.96 *dat.all.mod$alpha.sd

# Set up the levels for the locations how Fogarty has them.
dat.all.mod$location  <- factor(dat.all.mod$location, levels = c("North Sea","Irish Sea","Faroese","Barents Sea","Iceland","Eastern Scotian Shelf","Western Scotian Shelf","Eastern Georges Bank"))

# Now moving to the GAM models and looking at those residuals...
dat.all.mod$gam.resids <- NA
for(i in 1:n.stocks)
{
  dat.gam <- dat.all.mod %>% filter(stock == stocks[i])
  mod.gam <- gam(log.r.ssb ~ year, data= dat.gam)
  dat.all.mod$gam.resids[dat.all.mod$stock == stocks[i]] <-    residuals(mod.gam)
}

# Next lets get the acf for each time series, table needs the
acf.sr <- NULL
acf.gam <- NULL
tab.dat <- NULL 
for(i in 1:n.stocks)
{
dat.tmp <- dat.all.mod[dat.all.mod$stock == stocks[i],]
sr.acf<- acf(dat.tmp$resids,plot=F)$acf[-1,1,1]
len.sr.acf <- length(sr.acf)
gam.acf <- acf(dat.tmp$gam.resids,plot=F)$acf[-1,1,1]
len.gam.acf <- length(gam.acf)
# This extracts the lag 1 correlation for the table
tab.dat[[stocks[i]]] <- data.frame(Location = dat.tmp$location[1],Species = dat.tmp$Species[1],acf.sr = sr.acf[1],acf.gam = gam.acf[1])
acf.sr[[stocks[i]]] <- data.frame(stock = rep(stocks[i],len.sr.acf), 
                                  Species = rep(dat.tmp$Species[1],len.sr.acf), 
                                  Location = rep(dat.tmp$location[1],len.sr.acf),
                                  lag = 1:len.sr.acf,
                                  acf = sr.acf)
acf.gam[[stocks[i]]] <- data.frame(stock = rep(stocks[i],len.gam.acf), 
                                  Species = rep(dat.tmp$Species[1],len.gam.acf), 
                                  Location = rep(dat.tmp$location[1],len.gam.acf),
                                  lag = 1:len.gam.acf,
                                  acf = gam.acf)
}
tab.dat <- do.call("rbind",tab.dat)
tab.dat$acf.sr <- signif(tab.dat$acf.sr,digits=2)
tab.dat$acf.gam <- signif(tab.dat$acf.gam,digits=2)
acf.gam <- do.call("rbind",acf.gam)
acf.sr <- do.call("rbind",acf.sr)
acf.sr$cat <- "green"
acf.sr$cat[acf.sr$acf <=0] <-  'red'
acf.gam$cat <- "green"
acf.gam$cat[acf.gam$acf <=0] <- 'red'

# Next up I want to calculate the cross correlation between the recruit time series, on the log scale...

locations <- unique(dat$location)
n.locs <- length(locations)

ccf.tmp <- NULL
cory.tmp <- NULL
for(i in 1:n.locs)
{
dat.ccf <- dat %>% dplyr::filter(location == locations[i])
# Now need to get time series the same length and same years
cor.cod <- dat.ccf[dat.ccf$Species == "Cod",c("year","location","l.rec","Species")]
cor.had <- dat.ccf[dat.ccf$Species == "Haddock",c("year","location","l.rec","Species")]
# What years are in both datasets and subset it to that.
yr.cod <- cor.cod$year
yr.had <- cor.had$year

first.year <- max(c(min(yr.cod),min(yr.had)))
last.year <- min(c(max(yr.cod),max(yr.had)))
yr.range <- first.year:last.year
cor.cod <- cor.cod %>% dplyr::filter(year %in% yr.range)
cor.had <- cor.had %>% dplyr::filter(year %in% yr.range)

tst <- cor.test(cor.cod$l.rec,cor.had$l.rec)
ccf.mod <- ccf(cor.cod$l.rec,cor.had$l.rec,plot=FALSE)
ccf.tmp[[locations[i]]] <- cbind(lag=ccf.mod$lag, x.corr=ccf.mod$acf) %>% as_tibble() %>% mutate(cat=ifelse(x.corr>0,"green","red"))
ccf.tmp[[locations[i]]]$location <- locations[i]
cory.tmp[[locations[i]]] <- data.frame(Correlation = tst$estimate,lci = tst$conf.int[1], uci = tst$conf.int[2],location = locations[i])
}
dat.cory <- do.call('rbind',cory.tmp)
dat.ccf <- do.call("rbind",ccf.tmp)

# Set up the levels for the locations how Fogarty has them.
dat.cory$location  <- factor(dat.cory$location, levels = c("North Sea","Irish Sea","Faroese","Barents Sea","Iceland","Eastern Scotian Shelf","Western Scotian Shelf","Eastern Georges Bank"))
dat.ccf$location  <- factor(dat.ccf$location, levels = c("North Sea","Irish Sea","Faroese","Barents Sea","Iceland","Eastern Scotian Shelf","Western Scotian Shelf","Eastern Georges Bank"))
# and the levels for the table to get that in order we want.
tab.dat$Location <- factor(tab.dat$Location,levels = c("North Sea","Irish Sea","Faroese","Barents Sea","Iceland","Eastern Scotian Shelf","Western Scotian Shelf","Eastern Georges Bank"))
tab.dat <- tab.dat[order(tab.dat$Location),]

# Using the fun idea of using either the bottom 20% or 50% of the SSB values to estimate alpha
# We lose a lot of data with the 20% filter.
dat.20.alpha.cod <- dat.all.mod %>% dplyr::group_by(Period,location,.drop = F) %>% 
                                dplyr::filter(ssb.prop <= 0.2, Species == "Cod") %>% dplyr::summarise(alpha.20.cod = mean(log.r.ssb),
                                                                                                      lci.20.cod = mean(log.r.ssb) - sd(log.r.ssb),
                                                                                                      uci.20.cod = mean(log.r.ssb) + sd(log.r.ssb))
dat.20.alpha.had <- dat.all.mod %>% dplyr::group_by(Period,location,.drop = F) %>% 
                                dplyr::filter(ssb.prop <= 0.2, Species == "Haddock") %>% dplyr::summarise(alpha.20.had = mean(log.r.ssb),
                                                                                                      lci.20.had = mean(log.r.ssb) - sd(log.r.ssb),
                                                                                                      uci.20.had = mean(log.r.ssb) + sd(log.r.ssb))
# Combine
dat.20.alpha <- left_join(dat.20.alpha.cod,dat.20.alpha.had,by = c("Period","location"))


# We lose almost nothing with the 40% filter though
dat.40.alpha.cod <- dat.all.mod %>% dplyr::group_by(Period,location,.drop=F) %>% 
                            dplyr::filter(ssb.prop <= 0.4, Species == "Cod") %>% dplyr::summarise(alpha.40.cod = mean(log.r.ssb),
                                                                                                  lci.40.cod = mean(log.r.ssb) - sd(log.r.ssb),
                                                                                                  uci.40.cod = mean(log.r.ssb) + sd(log.r.ssb))

dat.40.alpha.had <- dat.all.mod %>% dplyr::group_by(Period,location,.drop=F) %>% 
                            dplyr::filter(ssb.prop <= 0.4, Species == "Haddock") %>% dplyr::summarise(alpha.40.had = mean(log.r.ssb),
                                                                                                      lci.40.had = mean(log.r.ssb) - sd(log.r.ssb),
                                                                                                      uci.40.had = mean(log.r.ssb) + sd(log.r.ssb))
dat.40.alpha <- left_join(dat.40.alpha.cod,dat.40.alpha.had,by = c("Period","location"))


# Now I want to do an analysis between cod/haddock stocks, but only using time series that are the same length, just to make sure that the time series length 
# isn't impacting our results.  I'll tidy up the dat.all.mod object to check this for both the alpha residuals and the gam residuals.



dat.trim <- NULL
for(i in 1:n.locs)
{
dat.tmp <- dat.all.mod %>% dplyr::filter(location == locations[i])
# Now need to get time series the same length and same years
dat.cod <- dat.tmp[dat.tmp$Species == "Cod",c("year","location","stock","Species",'Period','resids','gam.resids')]
dat.had <- dat.tmp[dat.tmp$Species == "Haddock",c("year","location","stock","Species",'Period','resids','gam.resids')]
# What years are in both datasets and subset it to that.
yr.cod <- dat.cod$year
yr.had <- dat.had$year

first.year <- max(c(min(yr.cod),min(yr.had)))
last.year <- min(c(max(yr.cod),max(yr.had)))
yr.range <- first.year:last.year
dat.cod <- dat.cod %>% dplyr::filter(year %in% yr.range)
dat.had <- dat.had %>% dplyr::filter(year %in% yr.range)
dat.trim[[locations[i]]] <- bind_rows(dat.cod,dat.had)

}


dat.trim.mod <- do.call("rbind",dat.trim)

```

**Here is Figure 2 from Fogarty, the Residual plot from the S-R models**

```{r sr-resid-plot,warning =F,echo=F,fig.width=11,fig.height=11,message=F,fig.cap = "Residuals from the Ricker Stock recruitment model."}

p <- ggplot(dat.all.mod %>% dplyr::filter(region == "Northeast Atlantic"),aes(y=resids, x= year,colour = Period,linetype = Species)) +    
              geom_line() + 
              facet_wrap(~location ,ncol=3,scales = 'free_y') + xlab("") + ylab("Residuals (S-R model)")  + 
              scale_color_manual(values = cols)  + 
              geom_hline(yintercept = 0, color='grey',linetype = 'dashed')+
              scale_x_continuous(limits = c(1945,2020),breaks = seq(1950,2020,by=10),labels = NULL) +
              theme(axis.title.y = element_text(hjust=0.25),
                    legend.position = c(0.85, 0.25), 
                    legend.title.align=1,
                    legend.text.align = 1,
                    legend.title = element_text(size=16),
                    legend.text = element_text(size=12),
                    #legend.key.size = unit(3,"line"),
                    legend.key.width = unit(3,"cm")) 

p1 <- ggplot(dat.all.mod %>% dplyr::filter(region=="Northwest Atlantic"),aes(y=resids, x= year,colour = Period,linetype = Species)) +
              geom_line() + geom_hline(yintercept = 0, color='grey',linetype = 'dashed')+
              scale_x_continuous(limits = c(1945,2020),breaks = seq(1950,2020,by=10)) +
              facet_wrap(~location ,ncol=3, scales = 'free_y') + xlab("Year") + ylab("")  + 
              scale_color_manual(values = cols) + theme(legend.position = "none")

sr.resid.plt <- plot_grid(p,p1,nrow=2,rel_heights = c(2,1))
sr.resid.plt
```


\newpage

**Here is the GAM residual plot, kind of Figure 2, but for the smoothed time series**

```{r gam-resid-plot,echo=F,warning =F,fig.width=11,fig.height=11,message=F,fig.cap = "Recruit residuals from the GAM model."}

p <- ggplot(dat.all.mod %>% dplyr::filter(region == "Northeast Atlantic"),aes(y=gam.resids, x= year,colour = Period,linetype = Species)) +    
              geom_line() + 
              facet_wrap(~location ,ncol=3,scales = 'free_y') + xlab("") + ylab("Residuals (GAM)")  + 
              scale_color_manual(values = cols)  + 
              geom_hline(yintercept = 0, color='grey',linetype = 'dashed')+
              scale_x_continuous(limits = c(1945,2020),breaks = seq(1950,2020,by=10),labels = NULL) +
              theme(axis.title.y = element_text(hjust=0.25),
                    legend.position = c(0.85, 0.25), 
                    legend.title.align=1,
                    legend.text.align = 1,
                    legend.title = element_text(size=16),
                    legend.text = element_text(size=12),
                    #legend.key.size = unit(3,"line"),
                    legend.key.width = unit(3,"cm")) 

p1 <- ggplot(dat.all.mod %>% dplyr::filter(region=="Northwest Atlantic"),aes(y=gam.resids, x= year,colour = Period,linetype = Species)) +
              geom_line() + geom_hline(yintercept = 0, color='grey',linetype = 'dashed')+
              scale_x_continuous(limits = c(1945,2020),breaks = seq(1950,2020,by=10)) +
              facet_wrap(~location ,ncol=3,scales = 'free_y') + xlab("Year") + ylab("")  + 
              scale_color_manual(values = cols) + theme(legend.position = "none")

gam.resid.plt <- plot_grid(p,p1,nrow=2,rel_heights = c(2,1))
gam.resid.plt
```


\newpage

**Next up is Figure 3, which will be the SD of the residuals from both the GAM and the S-R models, I will split this into 2 figures, the first being the S-R model SDs. The only way I can see getting a 95% CI around these would be to bootstrap them, but I don't see any real utility in doing that as it doesn't change our story at all.  I can do it, but not sure what it adds other than making the figure look more 'cool'.**

```{r sd-resid-sr,echo=F,warning=F,fig.width=11,fig.height=6,message=F,fig.cap = "Standard deviation of the log residuals from the Ricker S-R Model"}
sds.cod.sr <- dat.all.mod %>% dplyr::filter(Species == 'Cod') %>% dplyr::group_by(location,Period) %>% dplyr::summarise(sd = sd(resids))
# Toss Irish Sea Pre-1993 because we don't have a match with Haddock.
sds.cod.sr <- sds.cod.sr[!(sds.cod.sr$location == "Irish Sea" & sds.cod.sr$Period == "Pre 1993"),]
sds.had.sr <- dat.all.mod %>% dplyr::filter(Species == 'Haddock') %>% dplyr::group_by(location,Period) %>% dplyr::summarise(sd = sd(resids))
names(sds.cod.sr) <- c("location","Period","sd.cod")
names(sds.had.sr) <- c("location","Period","sd.had")
# Reorder the locations to match (or come close to matching) Fogarty
dat.sds.sr <- left_join(sds.cod.sr,sds.had.sr,by = c("location","Period"))

cols <- c("blue","firebrick2","green","grey","blue","firebrick2","green","grey")
shapes <- c(rep(21,4),rep(24,4))
p.sds <- ggplot(dat.sds.sr, aes(x=sd.cod,y=sd.had,fill = location,shape = location,color=location)) + geom_point(size=4) + facet_wrap(~Period) + 
            geom_abline(slope=1,intercept = 0) + scale_fill_manual(values = cols)+ scale_color_manual(values = cols)+scale_shape_manual(values = shapes) +
            xlab("Cod Residual SD (S-R model)") + ylab("Haddock Residual SD (S-R model)") +
            scale_x_continuous(limits=c(0.1,1.7)) + scale_y_continuous(limits=c(0.1,1.7)) + theme(legend.title = element_blank())
p.sds

```


\newpage

**Same figure as above, but only using data in which we have overlapping years of data between the stocks in a given location**

```{r sd-ts-same-resid-sr,echo=F,warning=F,fig.width=11,fig.height=6,message=F,fig.cap = "Standard deviation of the log residuals from the Ricker S-R Model but using residuals only from years in which data is found in both time series."}

sds.cod.sr <- dat.trim.mod %>% dplyr::filter(Species == 'Cod') %>% dplyr::group_by(location,Period) %>% dplyr::summarise(sd = sd(resids))
# Toss Irish Sea Pre-1993 because we don't have a match with Haddock.
sds.cod.sr <- sds.cod.sr[!(sds.cod.sr$location == "Irish Sea" & sds.cod.sr$Period == "Pre 1993"),]
sds.had.sr <- dat.trim.mod %>% dplyr::filter(Species == 'Haddock') %>% dplyr::group_by(location,Period) %>% dplyr::summarise(sd = sd(resids))
names(sds.cod.sr) <- c("location","Period","sd.cod")
names(sds.had.sr) <- c("location","Period","sd.had")
# Reorder the locations to match (or come close to matching) Fogarty
dat.sds.sr <- left_join(sds.cod.sr,sds.had.sr,by = c("location","Period"))

cols <- c("blue","firebrick2","green","grey","blue","firebrick2","green","grey")
shapes <- c(rep(21,4),rep(24,4))
p.sds.ts.same <- ggplot(dat.sds.sr, aes(x=sd.cod,y=sd.had,fill = location,shape = location,color=location)) + geom_point(size=4) + facet_wrap(~Period) + 
            geom_abline(slope=1,intercept = 0) + scale_fill_manual(values = cols)+ scale_color_manual(values = cols)+scale_shape_manual(values = shapes) +
            xlab("Cod Residual SD (S-R model)") + ylab("Haddock Residual SD (S-R model)") +
            scale_x_continuous(limits=c(0.1,1.7)) + scale_y_continuous(limits=c(0.1,1.7)) + theme(legend.title = element_blank())
p.sds.ts.same

```


\newpage


**Here are the SDs of the residuals from the GAMs.  The only way I can see getting a 95% CI around these would be to bootstrap them, but I don't see any real utility in doing that as it doesn't change our story at all.  I can do it, but not sure what it adds other than making the figure look more 'cool'.**

```{r sd-resid-gam,echo=F,warning=F,fig.width=11,fig.height=6,message=F,fig.cap = "Standard deviation of the log residuals from the GAMs"}

sds.cod.gam <- dat.all.mod %>% dplyr::filter(Species == 'Cod') %>% dplyr::group_by(location,Period) %>% dplyr::summarise(sd = sd(gam.resids))
# Toss Irish Sea Pre-1993 because we don't have a match with Haddock.
sds.cod.gam <- sds.cod.gam[!(sds.cod.gam$location == "Irish Sea" & sds.cod.gam$Period == "Pre 1993"),]
sds.had.gam <- dat.all.mod %>% dplyr::filter(Species == 'Haddock') %>% dplyr::group_by(location,Period) %>% dplyr::summarise(sd = sd(gam.resids))
names(sds.cod.gam) <- c("location","Period","sd.cod")
names(sds.had.gam) <- c("location","Period","sd.had")

dat.sds.gam <- left_join(sds.cod.gam,sds.had.gam,by = c("location","Period"))

cols <- c("blue","firebrick2","green","grey","blue","firebrick2","green","grey")
shapes <- c(rep(21,4),rep(24,4))

p.sds.gam <- ggplot(dat.sds.gam, aes(x=sd.cod,y=sd.had,fill = location,shape = location,color=location)) + geom_point(size=4) + facet_wrap(~Period) + 
            geom_abline(slope=1,intercept = 0) + scale_fill_manual(values = cols)+ scale_color_manual(values = cols)+scale_shape_manual(values = shapes) +
            xlab("Cod Residual SD (GAM)") + ylab("Haddock Residual SD (GAM)") +
            scale_x_continuous(limits=c(0.1,2)) + scale_y_continuous(limits=c(0.1,2))
p.sds.gam

```


\newpage

**Same figure as above, but only using data in which we have overlapping years of data between the stocks in a given location**

```{r sd-ts-same-resid-gam,echo=F,warning=F,fig.width=11,fig.height=6,message=F,fig.cap = "Standard deviation of the log residuals from the GAMs but using residuals only from years in which data is found in both time series."}

sds.cod.gam <- dat.trim.mod %>% dplyr::filter(Species == 'Cod') %>% dplyr::group_by(location,Period) %>% dplyr::summarise(sd = sd(gam.resids))
# Toss Irish Sea Pre-1993 because we don't have a match with Haddock.
sds.cod.gam <- sds.cod.gam[!(sds.cod.gam$location == "Irish Sea" & sds.cod.gam$Period == "Pre 1993"),]
sds.had.gam <- dat.trim.mod %>% dplyr::filter(Species == 'Haddock') %>% dplyr::group_by(location,Period) %>% dplyr::summarise(sd = sd(gam.resids))
names(sds.cod.gam) <- c("location","Period","sd.cod")
names(sds.had.gam) <- c("location","Period","sd.had")

dat.sds.gam <- left_join(sds.cod.gam,sds.had.gam,by = c("location","Period"))

cols <- c("blue","firebrick2","green","grey","blue","firebrick2","green","grey")
shapes <- c(rep(21,4),rep(24,4))

p.sds.gam.ts.same <- ggplot(dat.sds.gam, aes(x=sd.cod,y=sd.had,fill = location,shape = location,color=location)) + geom_point(size=4) + facet_wrap(~Period) + 
            geom_abline(slope=1,intercept = 0) + scale_fill_manual(values = cols)+ scale_color_manual(values = cols)+scale_shape_manual(values = shapes) +
            xlab("Cod Residual SD (GAM)") + ylab("Haddock Residual SD (GAM)") +
            scale_x_continuous(limits=c(0.1,2)) + scale_y_continuous(limits=c(0.1,2))
p.sds.gam.ts.same

```


\newpage


**Table with the ACF values in it, both from SR and from GAM residuals **

```{r, tab-acf,echo=F}

print(tab.dat)
```


\newpage

**Now lets get the Correlation between the time series, Figure 4**

```{r cross-cor,echo=F,fig.width=8,fig.height=8,message=F,fig.cap ="Cross correlation of the recruiment (log scale) time series"}

p.cor <- ggplot(dat.cory,aes(y=Correlation,x=location)) + geom_point(size=4) + 
              geom_errorbar(aes(ymin =lci,ymax=uci),width=0) + 
              geom_hline(yintercept = 0, linetype='dashed',color='grey') +
              theme(axis.text.x = element_text(angle = 45, hjust = 1.,size=16)) + xlab("")
p.cor

```


\newpage


**Figure 5 is the Alpha from the Stock Recruitment models, now will be 2 panels.**

```{r sr-alpha-plot,echo=F,fig.width=11,fig.height=6,message=F,fig.cap = "Estimated log(alpha) from Ricker Stock Recruitment models for each stock in the Pre 1993 and Recent period."}

# This is super ugly....
dat.cur <- NULL;dat.past <- NULL
for(i in 1:n.stocks) dat.cur[[stocks[i]]] <- dat.alpha[dat.alpha$Period == "Recent" & dat.alpha$stock  == stocks[i],][1,]
for(i in 1:n.stocks) dat.past[[stocks[i]]] <- dat.alpha[dat.alpha$Period == "Pre 1993" & dat.alpha$stock  == stocks[i],][1,]

dat.cur <- do.call('rbind',dat.cur)
dat.past <- do.call('rbind',dat.past)
dat.tmp <- rbind(dat.cur,dat.past)
d.alp <- dat.tmp %>% dplyr::select(Species,location,alpha,LCI,UCI,stock,Period)
d.alp <- d.alp[!is.na(d.alp$Species),]
d.had <- d.alp[d.alp$Species == "Haddock",]
#d.had <- d.had[!is.na(d.had$Species),]

d.cod <- d.alp[d.alp$Species == "Cod",]
#d.cod <- d.cod[!is.na(d.cod$Species),]
d.cod <- d.cod[!(d.cod$location == "Irish Sea" & d.cod$Period == "Pre 1993"),]

names(d.had) <- c("Species","location","alpha.had","LCI.had","UCI.had",'stock','Period')
names(d.cod) <- c("Species","location","alpha.cod","LCI.cod","UCI.cod",'stock',"Period")
d.merge <- data.frame(location = d.had$location, 
                      Period = d.had$Period,
                      alpha.had = d.had$alpha.had,
                      LCI.had = d.had$LCI.had,
                      UCI.had = d.had$UCI.had,
                      alpha.cod = d.cod$alpha.cod,
                      LCI.cod = d.cod$LCI.cod,
                      UCI.cod = d.cod$UCI.cod)
# Order these like Fogarty
d.merge$location  <- factor(d.merge$location, levels = c("North Sea","Irish Sea","Faroese","Barents Sea","Iceland","Eastern Scotian Shelf","Western Scotian Shelf","Eastern Georges Bank"))


# SO this is the wrong figure, cause I want to make this plot using the SD of the residuals from the SR.  
# But maybe I want to make a plot using these somehow....
alpha.plt <- ggplot(d.merge,aes(y = alpha.had,x=alpha.cod,fill = location,shape = location,color=location)) + geom_point(size=4) + facet_wrap(~Period) +
     geom_errorbar(aes(ymin=LCI.had,ymax=UCI.had)) +
     geom_errorbarh(aes(xmin = LCI.cod,xmax=UCI.cod)) +
     scale_fill_manual(values = cols)+ scale_color_manual(values = cols)+scale_shape_manual(values = shapes) +
     geom_abline(slope=1,intercept = 0) + 
     xlab("Cod log(alpha)") + ylab("Haddock log(alpha)")
alpha.plt

```


\newpage

**This figure is the frequency of the SSB data by stock and era showing where data lands in terms of SSB, I show figure with 20% and 40% cut offs., data is binned into 10 bins (so about every 0.1 is a bin)**

```{r hist-rec-ssb, echo = F,fig.width=11,fig.height=11,message=F,fig.cap = "Here is a density plot of the SSB values by each period.  Vertical grey dashed line is the SSB of 0.2 while the grey solid vertical line is 0.4."}

p.freq <- ggplot(data = dat.all.mod) + geom_freqpoly(aes(x = ssb.prop,color=Period),position='stack',bins=10,size=2) + scale_color_manual(values = c("blue","firebrick2"))+
              facet_wrap(~stock) + geom_vline(xintercept = 0.2,color='grey',linetype='dashed',size=1.5) + geom_vline(xintercept = 0.4,color='grey',size=1.25) + 
              xlab("Proportion of Max SSB")
p.freq

```


\newpage


**"Alpha" using the mean of the log(Rec/SSB) for SSB of <= 0.2 of maximum SSB**

```{r, alpha-20-plt,echo=F,message =F, warning =F,fig.width=11,fig.height=6,message=F,fig.cap = "The mean log(Rec/SSB) when SSB is <= 0.2 of maximum ssb"}
alpha.20.plt <- ggplot(dat.20.alpha,aes(y = alpha.20.had,x=alpha.20.cod,fill = location,shape = location,color=location)) + geom_point(size=4) + facet_wrap(~Period) +
     geom_errorbar(aes(ymin=lci.20.had,ymax=uci.20.had)) +
     geom_errorbarh(aes(xmin = lci.20.cod,xmax=uci.20.cod)) +
     scale_fill_manual(values = cols)+ scale_color_manual(values = cols)+scale_shape_manual(values = shapes) +
     geom_abline(slope=1,intercept = 0) + 
     xlab("Cod mean(log(rec/ssb)) for ssb < 0.2 of max") + ylab("Haddock mean(log(rec/ssb)) for ssb < 0.2 of max")
alpha.20.plt

```


\newpage

**"Alpha" using the mean of the log(Rec/SSB) for SSB of <= 0.4 of maximum SSB**

```{r, alpha-40-plt,message =F, warning =F,echo=F,fig.width=11,fig.height=6,message=F,fig.cap = "The mean log(Rec/SSB) when SSB is <= 0.2 of maximum ssb"}
alpha.40.plt <- ggplot(dat.40.alpha,aes(y = alpha.40.had,x=alpha.40.cod,fill = location,shape = location,color=location)) + geom_point(size=4) + facet_wrap(~Period) +
     geom_errorbar(aes(ymin=lci.40.had,ymax=uci.40.had)) +
     geom_errorbarh(aes(xmin = lci.40.cod,xmax=uci.40.cod)) +
     scale_fill_manual(values = cols)+ scale_color_manual(values = cols)+scale_shape_manual(values = shapes) +
     geom_abline(slope=1,intercept = 0) + 
     xlab("Cod mean(log(rec/ssb)) for ssb < 0.4 of max") + ylab("Haddock mean(log(rec/ssb)) for ssb < 0.4 of max")
alpha.40.plt

```


\newpage


# Appendix

**The fits of the Ricker S-R model, first is the one with two periods**

```{r rssb-ssb-setup, echo =F,include =F,message=F}

# Now the Rec/SSB vs SSB figure, with a line of best fit, not ugly at all....
p0 <- ggplot(dat %>% dplyr::filter(region == "Northeast Atlantic"),aes(y=rec.ssb, x= ssb,colour = Period,shape = Species,linetype = Species)) + geom_point(size=2) + 
              facet_wrap(~location ,scales = 'free_x',ncol=3) + xlab("") + ylab("Recruits/SSB")  + 
              scale_color_manual(values = cols)  + scale_linetype_manual(values = lty) + scale_y_log10() + 
              geom_smooth(method = 'lm') + scale_x_continuous(limits = c(0,NA)) +
#              scale_x_continuous(limits = c(1945,2020),breaks = seq(1950,2020,by=10)) +
#              geom_vline(xintercept = 1992.5,color = "grey",size =2) + 
              theme(axis.title.y = element_text(hjust=0),
                    legend.position = c(0.85, 0.25), 
                    legend.title.align=1,
                    legend.text.align = 1,
                    legend.title = element_text(size=16),
                    legend.text = element_text(size=12),
                    #legend.key.size = unit(3,"line"),
                    legend.key.width = unit(3,"cm")) + guides(#shape = guide_legend(override.aes = list(size=0),title.position = "top"),
                                                              linetype = guide_legend(override.aes = list(size=1,color='black'))
                                                              )
# Now do this to make the symbol larger than the line thickness in the legend, wild!
p0
# This does something funky
grid::grid.ls(grid::grid.force())

# Set the size of the point in the legend to 2 mm
grid::grid.gedit("key-[-0-9]-1-1", size = unit(4, "mm"))

# save the modified plot to an object
p.tidy <- grid::grid.grab()

# Now the NW Atlantic stocks
p1 <- ggplot(dat %>% dplyr::filter(region == "Northwest Atlantic"),aes(y=rec.ssb, x= ssb,colour = Period,shape = Species,linetype = Species)) + geom_point(size=2) + 
              facet_wrap(~ location ,scales = 'free',ncol=3) + xlab("SSB (tonnes)") + ylab("")  + 
              scale_color_manual(values = cols)  + scale_linetype_manual(values = lty) + scale_y_log10() + 
              geom_smooth(method = 'lm') + scale_x_continuous(limits = c(0,NA)) +
#              scale_x_continuous(limits = c(1945,2020),breaks = seq(1950,2020,by=10)) +
#              geom_vline(xintercept = 1992.5, color ='grey',size=3)+
              theme(legend.position = "none")
# And combo them
p.rec.per.ssb <- plot_grid(p.tidy,p1,nrow=2,rel_heights = c(2,1))
```

```{r rssb-ssb-plot, echo =F,fig.width=11,fig.height=11,message=F,fig.cap = "Recruits/SSB (log scale) vs SSB, Linear model fit on log(10) scale with Alpha calculated for pre 1993 and recent periods"}
p.rec.per.ssb
```


\newpage


**Now the S-R model with just the one period**

```{r rssb-ssb-all-plot, echo =F,message=F,fig.width=11,fig.height=11,message=F,fig.cap = "Recruits/SSB (log scale) vs SSB, Linear model fit on log(10) scale with no differentiation between Periods.  Used for Residual analyses."}

# Now the Rec/SSB vs SSB figure, with a line of best fit, not ugly at all....
p0 <- ggplot(dat %>% dplyr::filter(region == "Northeast Atlantic"),aes(y=rec.ssb, x= ssb,color=Species,shape = Species,linetype = Species)) + geom_point(size=2) + 
              facet_wrap(~location ,scales = 'free_x',ncol=3) + xlab("") + ylab("Recruits/SSB")  + 
              scale_color_manual(values = cols)  + scale_linetype_manual(values = lty) + scale_y_log10() + 
              geom_smooth(method = 'lm') + scale_x_continuous(limits = c(0,NA)) +
#              scale_x_continuous(limits = c(1945,2020),breaks = seq(1950,2020,by=10)) +
#              geom_vline(xintercept = 1992.5,color = "grey",size =2) + 
              theme(axis.title.y = element_text(hjust=0),
                    legend.position = c(0.85, 0.25), 
                    legend.title.align=1,
                    legend.text.align = 1,
                    legend.title = element_text(size=16),
                    legend.text = element_text(size=12),
                    #legend.key.size = unit(3,"line"),
                    legend.key.width = unit(3,"cm"))

# Now the NW Atlantic stocks
p1 <- ggplot(dat %>% dplyr::filter(region == "Northwest Atlantic"),aes(y=rec.ssb, x= ssb,color = Species,linetype = Species,shape=Species)) + geom_point(size=2) + 
              facet_wrap(~ location ,scales = 'free',ncol=3) + xlab("SSB (tonnes)") + ylab("")  + 
              scale_color_manual(values = cols)  + scale_linetype_manual(values = lty) + scale_y_log10() + 
              geom_smooth(method = 'lm') + scale_x_continuous(limits = c(0,NA)) +
#              scale_x_continuous(limits = c(1945,2020),breaks = seq(1950,2020,by=10)) +
#              geom_vline(xintercept = 1992.5, color ='grey',size=3)+
              theme(legend.position = "none")
# And combo them
p.rec.per.ssb.all <- plot_grid(p0,p1,nrow=2,rel_heights = c(2,1))
p.rec.per.ssb.all
```


\newpage

**Here are the GAM fits from the Recruit time series, GAMs were fit on the log scale**

```{r gam-rec, message = F,warning=F,echo =F,fig.width=11,fig.height=11,fig.cap= "Recruitment (in millons) time series for 8 Atlantic Cod and Haddock stocks in the Atlantic Ocean.  The vertical grey line indicates the division between the two periods.  The lines are the GAM fits with 95% CI in the shaded region"}
# Recruits vs SSB
p0 <- ggplot(dat %>% dplyr::filter(region == "Northeast Atlantic"),aes(y=recruits/1000, x= year,shape = Species,color=Species,linetype=Species)) + geom_point(size=2) + 
              facet_wrap(~location ,scales = 'free',ncol=3) + xlab("") + ylab("Recruits (Number in Millons)")  + 
              scale_color_manual(values = cols)  + scale_linetype_manual(values = lty) + scale_y_log10() + 
              scale_x_continuous(limits = c(1945,2020),breaks = seq(1950,2020,by=10)) +
              geom_smooth(method = 'gam') + 
              geom_vline(xintercept = 1992.5,color = "grey",size =2) + 
              theme(axis.title.y = element_text(hjust=0),
                    legend.position = c(0.85, 0.25), 
                    legend.title.align=1,
                    legend.text.align = 1,
                    legend.title = element_text(size=16),
                    legend.text = element_text(size=12),
                    legend.key.width = unit(3,"cm")) + guides(colour = guide_legend(override.aes = list(size=1.5),title.position = "top"))

# Now the NW Atlantic stocks
p1 <- ggplot(dat %>% dplyr::filter(region == "Northwest Atlantic"),aes(y=recruits/1000, x= year,shape = Species,color=Species,linetype=Species)) + geom_point(size=2) +
              facet_wrap(~ location ,scales = 'free',ncol=3) + xlab("Year") + ylab("")  + 
              scale_color_manual(values = cols)  + scale_linetype_manual(values = lty) + scale_y_log10() + 
              geom_smooth(method = 'gam') + 
              scale_x_continuous(limits = c(1945,2020),breaks = seq(1950,2020,by=10)) +
              geom_vline(xintercept = 1992.5, color ='grey',size=3)+
              theme(legend.position = "none")

p.rec.gam <- plot_grid(p0,p1,nrow=2,rel_heights = c(2,1))
p.rec.gam
```


\newpage


**We can make a cross-correlation figure by region to if we want**

```{r ccf-plot,message = F,warning=F,echo =F,fig.width=8,fig.height=8,fig.cap= "Cross correlation of recruitment time series for all location."}

p.ccf <- ggplot(data = dat.ccf,aes(x=lag,y=x.corr)) + facet_wrap(~location) +
              geom_bar(stat="identity",aes(fill=cat))+
              scale_fill_manual(values=c("#339933","#cc0000"))+
              ylab("Cross correlation")+
              scale_y_continuous(limits=c(-1,1))+
              theme(legend.position = "none", plot.title=element_text(size=10))
p.ccf

```


\newpage

**ACF figure for the full SR model residuals**

```{r acf-sr-plot,message = F,warning=F,echo =F,fig.width=11,fig.height=11,fig.cap= "Autocorrelation of recruitment residuals from the full stock recruitment model for each stock."}

p.acf.sr <- ggplot(data = acf.sr,aes(x=lag,y=acf)) + facet_wrap(~stock) +
              geom_bar(stat="identity",aes(fill=cat))+
              scale_fill_manual(values=c("#339933","#cc0000"))+
              ylab("Cross correlation")+
              scale_y_continuous(limits=c(-1,1))+
              theme(legend.position = "none", plot.title=element_text(size=10))
p.acf.sr

```


\newpage

** ACF figure for the GAM model residuals**

```{r acf-gam-plot,message = F,warning=F,echo =F,fig.width=11,fig.height=11,fig.cap= "Autocorrelation of recruitment residuals from the GAMs for each stock."}

p.acf.gam <- ggplot(data = acf.gam,aes(x=lag,y=acf)) + facet_wrap(~stock) +
              geom_bar(stat="identity",aes(fill=cat))+
              scale_fill_manual(values=c("#339933","#cc0000"))+
              ylab("Cross correlation")+
              scale_y_continuous(limits=c(-1,1))+
              theme(legend.position = "none", plot.title=element_text(size=10))
p.acf.gam

```
